\plaintitle

### 2018-04-03 paper/paper.tex
...

\begin{enumerate}
% 各種技術を組み合わせた翻訳支援というパラダイムの提案
\item Introduction of a ``translation paradigm'' to control a machine from vague specifications
\item IME-like command etnry system
% やりたいことを実行するインタフェース (IME的なもの)
\item Flexible dynamic search system based on RegExp (ExpandHelp)
% そのための柔軟なインフラ (ExpandHelp)
\item Data sharing infrastructure for the translation paradigm
% 共有/編集しやすい正規表現DSLとそのインプリ(Scrapbox+)
% \item これが唯一の解決法ではないが、こういう考え方がポピュラーになって欲しい
\end{enumerate}

@@

\begin{quotation}
  \begin{verbatim}
    $ git diff README.md
    $ xxx
  \end{verbatim}
\end{quotation}

@@

\begin{figure}[b]
  \includegraphics[width=8cm,bb=0 0 976 670]{figures/nyuuryoku-ime.png}
  \caption{Example IM for Japanese text input.}
  \label{bash1}
\end{figure}

@@

Gitsome(https://github.com/donnemartin/gitsome)
helps \texttt{git} users by
showing possible arguments and manuals on the Unix shell,
just like {\GH}.
The direction is alomost the same as {\GH}, but
Gitsome does not support .....

>>>>

\begin{enumerate}
% 各種技術を組み合わせた翻訳支援というパラダイムの提案
\item Introduction of ``\textit{translation paradigm}'' for
  generating a correct instruction to a machine from
  the user's vague intention
\item IME-like command etnry system
% やりたいことを実行するインタフェース (IME的なもの)
\item Flexible dynamic search system based on RegExp (ExpandHelp)
% そのための柔軟なインフラ (ExpandHelp)
\item Data sharing infrastructure for the translation paradigm
% 共有/編集しやすい正規表現DSLとそのインプリ(Scrapbox+)
% \item これが唯一の解決法ではないが、こういう考え方がポピュラーになって欲しい
\end{enumerate}

@@

\begin{quotation}
\begin{verbatim}
$ git diff README.md
$
\end{verbatim}
\end{quotation}

@@

\begin{figure}[h]
  \includegraphics[width=8cm,bb=0 0 976 670]{figures/nyuuryoku-ime.png}
  \caption{An IM for Japanese text input.}
  \label{bash1}
\end{figure}

@@

Gitsome(https://github.com/donnemartin/gitsome)
helps \texttt{git} users by
showing possible arguments and manuals on the Unix shell,
just like {\GH}.
The goal of Git some is alomost the same as {\GH}, but
Gitsome does not support ...
